Measurement and Probability in Fuzzy Quantum Theories

### 2017-06-18 prop_iop.tex
prop_iop.tex \subsection{From Real-valued to Interval-valued I} Updating

>>>>

\begin{example}For any positive integer~$n$, there is an additive
interval-valued function\nb$\widehat{\iota}_{n}:\left[0,1\right]\rightarrow\widehat{\mathscr{I}}_{n}$
defined by the following:
\begin{itemize}
\item when $x=0$ or $x=1$, $\widehat{\iota}_{n}\left(x\right)=\left[x,x\right]$;
\item when $0<x<1$, we have $\widehat{\iota}_{n}\left(x\right)=\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]$,
where $k$ is defined by either one of the following:
\begin{itemize}
\item $2\mid k$ and $k-0.5\le2nx\le k+0.5$;
\item $2\nmid k$ and $k-0.5<2nx<k+0.5$,
\end{itemize}
\end{itemize}
where $\widehat{\mathscr{I}}_{n}=\set{\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\cup\left\{ \left[0,0\right],\left[1,1\right]\right\} $.\end{example}

\begin{proof}~
\begin{itemize}
\item $\widehat{\iota}_{n}\left(0\right)=\left[0,0\right]$. 
\item $\widehat{\iota}_{n}\left(1\right)=\left[1,1\right]$. 
\item When $x=0$ or $x=1$, we have $\widehat{\iota}_{n}\left(1-x\right)=\left[1-x,1-x\right]=\left[1,1\right]-\widehat{\iota}_{n}\left(x\right)$.
Otherwise, since $2\mid k\Leftrightarrow2\mid\left(2n-k\right)$,
we always have
\begin{equation}
\widehat{\iota}_{n}\left(1-x\right)=\left[1-\frac{k+1}{2n},1-\frac{k-1}{2n}\right]\cap\left[0,1\right]=\left[1,1\right]-\widehat{\iota}_{n}\left(x\right)\textrm{ .}
\end{equation}
\item It is sufficient to prove the case when $N=2$, i.e., for a set $\left\{ x_{1},x_{2}\right\} \subseteq\left[0,1\right]$,
if $x_{1}+x_{2}\in\left[0,1\right]$, then $\widehat{\iota}_{n}\left(x_{1}+x_{2}\right)\subseteq\widehat{\iota}_{n}\left(x_{1}\right)+\widehat{\iota}_{n}\left(x_{2}\right)$,
and the rest can be done by the induction. 
\begin{itemize}
\item When $x_{1}=0$, we have $\widehat{\iota}_{n}\left(x_{1}+x_{2}\right)=\widehat{\iota}_{n}\left(x_{2}\right)=\widehat{\iota}_{n}\left(x_{1}\right)+\widehat{\iota}_{n}\left(x_{2}\right)$.
\item When $x_{1}=1$, we must have $x_{2}=0$ which reduces to the previous
case.
\item When $\widehat{\iota}_{n}\left(x_{1}\right)=\left[\frac{k_{1}-1}{2n},\frac{k_{1}+1}{2n}\right]\cap\left[0,1\right]$
and $\widehat{\iota}_{n}\left(x_{2}\right)=\left[\frac{k_{2}-1}{2n},\frac{k_{2}+1}{2n}\right]\cap\left[0,1\right]$,
we have $k_{1}-0.5\le2nx_{1}\le k_{1}+0.5$ and $k_{2}-0.5\le2nx_{2}\le k_{2}+0.5$
so that $k_{1}+k_{2}-1\le2n\left(x_{1}+x_{2}\right)\le k_{1}+k_{2}+1$.
Hence, no matter whether $x_{1}+x_{2}=1$ or not, we always have 
\begin{equation}\eqalign{ 
& \widehat{\iota}_{n}\left(x_{1}+x_{2}\right)\subseteq\left[\frac{k_{1}+k_{2}-2}{2n},\frac{k_{1}+k_{2}+2}{2n}\right]\cap\left[0,1\right]\\ 
= &\left[\frac{k_{1}-1}{2n},\frac{k_{1}+1}{2n}\right]\cap\left[0,1\right]+\left[\frac{k_{2}-1}{2n},\frac{k_{2}+1}{2n}\right]\cap\left[0,1\right]\\
= &\widehat{\iota}_{n}\left(x_{1}\right)+\widehat{\iota}_{n}\left(x_{2}\right)\textrm{ .} 
}\end{equation}
\end{itemize}
\end{itemize}
\end{proof}
